---
title: "M2 thesis for publication"
author: "Johannes Ahlström"
date: "30 june 2017"
output: word_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(readxl)
library(stats)
library(car)
library(MASS)
```

```{r}
FINAL_FILE_FOR_MULTIPLE_REGRESSION <- read_excel("C:/Users/johannes/Desktop/FINAL FILE FOR MULTIPLE REGRESSION1.xlsx", sheet = "all variables")
df1<-na.omit(FINAL_FILE_FOR_MULTIPLE_REGRESSION)
df1[,1]<-NULL
df1[,1]<-NULL
```

```{r}
fun <- function(x){
  quantiles <- quantile( x, c(.05, .95 ) )
  x[ x < quantiles[1] ] <- quantiles[1]
  x[ x > quantiles[2] ] <- quantiles[2]
  x
}
```

```{r}
df<-as.data.frame(apply(df1,2,fun))
```


```{r}
m05 <- df[, c(6:15)]
m06 <- df[, c(17:26)]
m07 <- df[, c(28:37)]
m08 <- df[, c(39:48)]
m09 <- df[, c(50:59)]
m10 <- df[, c(61:70)]
m11 <- df[, c(72:81)]
m12 <- df[, c(83:92)]
m13 <- df[, c(94:103)]
m14 <- df[, c(105:114)]
```

```{r}
print(names(df))
```

```{r}
print(summary.data.frame(df))
```

Means

```{r}

round(sapply(df, mean),2)

```

Standard Deviations

```{r}
round(sapply(df, sd),2)
```

Variances

```{r}
round(sapply(df, var),2)
```


```{r}
#Histograms CSR
hist(df$CSR2006)
hist(df$CSR2007)
hist(df$CSR2008)
hist(df$CSR2009)
hist(df$CSR2010)
hist(df$CSR2011)
hist(df$CSR2012)
hist(df$CSR2013)
hist(df$CSR2014)
hist(df$CSR2015)
```

#Histograms independents#
```{r}
#Histograms independents#
for ( i in seq(1,length( m05 ),1) ) hist(m05[,i],xlab = NULL,main=names(m05[i]))
```
```{r}
for ( i in seq(1,length( m06 ),1) ) hist(m06[,i],xlab = NULL,main=names(m06[i]))
```
```{r}
for ( i in seq(1,length( m07 ),1) ) hist(m07[,i],xlab = NULL,main=names(m07[i]))
```
```{r}
for ( i in seq(1,length( m08 ),1) ) hist(m08[,i],xlab = NULL,main=names(m08[i]))
```
```{r}
for ( i in seq(1,length( m09 ),1) ) hist(m09[,i],xlab = NULL,main=names(m09[i]))
```
```{r}
for ( i in seq(1,length( m10 ),1) ) hist(m10[,i],xlab = NULL,main=names(m10[i]))
```
```{r}
for ( i in seq(1,length( m11 ),1) ) hist(m11[,i],xlab = NULL,main=names(m11[i]))
```
```{r}
for ( i in seq(1,length( m12 ),1) ) hist(m12[,i],xlab = NULL,main=names(m12[i]))
```
```{r}
for ( i in seq(1,length( m13 ),1) ) hist(m13[,i],xlab = NULL,main=names(m13[i]))
```
```{r}
for ( i in seq(1,length( m14 ),1) ) hist(m14[,i],xlab = NULL,main=names(m14[i]))
```


```{r}
for ( i in seq(1,length( m05 ),1)) scatterplot(m05[,i],df$CSR2006,xlab=names(m05[i]),main=names(m05[i]))
```
```{r}
for ( i in seq(1,length( m06 ),1)) scatterplot(m06[,i],df$CSR2007,xlab=names(m06[i]),main=names(m06[i]))
```
```{r}
for ( i in seq(1,length( m07 ),1)) scatterplot(m07[,i],df$CSR2008,xlab=names(m07[i]),main=names(m07[i]))
```
```{r}
for ( i in seq(1,length( m08 ),1)) scatterplot(m08[,i],df$CSR2009,xlab=names(m08[i]),main=names(m08[i]))
```
```{r}
for ( i in seq(1,length( m09 ),1)) scatterplot(m09[,i],df$CSR2010,xlab=names(m09[i]),main=names(m09[i]))
```
```{r}
for ( i in seq(1,length( m10 ),1)) scatterplot(m10[,i],df$CSR2011,xlab=names(m10[i]),main=names(m10[i]))
```
```{r}
for ( i in seq(1,length( m11 ),1)) scatterplot(m11[,i],df$CSR2012,xlab=names(m11[i]),main=names(m11[i]))
```
```{r}
for ( i in seq(1,length( m12 ),1)) scatterplot(m12[,i],df$CSR2013,xlab=names(m12[i]),main=names(m12[i]))
```
```{r}
for ( i in seq(1,length( m13 ),1)) scatterplot(m13[,i],df$CSR2014,xlab=names(m13[i]),main=names(m13[i]))
```
```{r}
for ( i in seq(1,length( m14 ),1)) scatterplot(m14[,i],df$CSR2015,xlab=names(m14[i]),main=names(m14[i]))
```


Individual correlation matrices
2005 independents
```{r}
round(cor(m05),1)
```

2006 independents
```{r}
round(cor(m06),1)
```

2007 independents
```{r}
round(cor(m07),1)
```

2008 independents
```{r}
round(cor(m08),1)
```

2009 independents
```{r}
round(cor(m09),1)
```

2010 independents
```{r}
round(cor(m10),1)
```

2011 independents
```{r}
round(cor(m11),1)
```

2012 independents
```{r}
round(cor(m12),1)
```

2013 independents
```{r}
round(cor(m13),1)
```

2014 independents
```{r}
round(cor(m14),1)
```

Models
First model spec 2006-2005
```{r, model 1 spec 2006-2005}
#Model
fit06_05<- lm(df$CSR2006~df$`FCF/sales2005`+df$`FCF/employee2005`+df$ROA2005+df$ROE2005+df$`Net PM2005`+df$`Debt/Equity2005`+df$Sweden_dummy+df$Denmark_dummy+df$Finland_dummy+df$Norway_dummy)

#Stepwise regression
step06_05 <- stepAIC(fit06_05, direction="both")
step06_05$anova # display result

```

Second model spec 2006-2005
```{r,model 2 spec 2006-2005,}
#Model
fit2_06_05<-lm(df$CSR2006 ~ df$`FCF/sales2005` + df$`Net PM2005` + df$Denmark_dummy)

#Anova
print(Anova(fit2_06_05))

#Summary
print(summary(fit2_06_05))

# Autocorrelation
vif(fit2_06_05)
sqrt(vif(fit2_06_05))

##Non constant variance (Heteroscedasticity),
plot(fit2_06_05$residuals)
ncvTest(fit2_06_05)

##Non Normality (model)
qqPlot(fit2_06_05, main = "Q-Q plot")
sresid06_05<-studres(fit2_06_05)
hist(sresid06_05, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid06_05<-na.omit(sresid06_05)
xfit<-seq(min(na.sresid06_05), max(na.sresid06_05), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_06_05)
qqPlot(fit2_06_05,main = "Q-Q Plot")
leveragePlots(fit2_06_05)
```

FIrst model spec 2007-2006
```{r,model 1 spec 2007-2006,}
 
#Model
fit07_06<- lm(df$CSR2007~df$`FCF/sales2006`+df$`FCF/employee2006`+df$ROA2006+df$ROE2006+df$`Net PM2006`+df$`Debt/Equity2006`+df$Sweden_dummy +df$Denmark_dummy + df$Finland_dummy + df$Norway_dummy)

#Stepwise regression
step07_06 <- stepAIC(fit07_06, direction="both")
step07_06$anova # display result

```

Second model 2007-2006

```{r, model 2 spec 2007-2006}
#Model
fit2_07_06<-lm(df$CSR2007 ~ df$`FCF/sales2006` + df$`FCF/employee2006` + df$ROA2006 + df$`Net PM2006` + df$Denmark_dummy)
#Anova
print(Anova(fit2_07_06))

#Summary
print(summary(fit2_07_06))

# Autocorrelation
vif(fit2_07_06)
sqrt(vif(fit2_07_06))

##Non constant variance (Heteroscedasticity),
plot(fit2_07_06$residuals)
ncvTest(fit2_07_06)

##Non Normality (model)
qqPlot(fit2_07_06, main = "Q-Q plot")
sresid07_06<-studres(fit2_07_06)
hist(sresid07_06, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid07_06<-na.omit(sresid07_06)
xfit<-seq(min(na.sresid07_06), max(na.sresid07_06), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_07_06)
qqPlot(fit2_07_06,main = "Q-Q Plot")
leveragePlots(fit2_07_06)


```

First model 2008-2007

```{r, model 1 2008 2007}
  #Model
fit08_07<- lm(df$CSR2008~df$`FCF/sales2007`+df$`FCF/employee2007`+df$ROA2007+df$ROE2007+df$`Net PM2007`+df$`Debt/Equity2007`+df$Sweden_dummy +df$Denmark_dummy + df$Finland_dummy + df$Norway_dummy)

#Stepwise regression
step08_07 <- stepAIC(fit08_07, direction="both")
step08_07$anova # display result
```
Second model 2008-2007
```{r, model 2 2008 2007}

#Model
fit2_08_07<-lm(df$CSR2008 ~ df$`FCF/sales2007` + df$`FCF/employee2007` + df$`Net PM2007` + df$Denmark_dummy)
#Anova
print(Anova(fit2_08_07))

#Summary
print(summary(fit2_08_07))

# Autocorrelation
vif(fit2_08_07)
sqrt(vif(fit2_08_07))

##Non constant variance (Heteroscedasticity),
plot(fit2_08_07$residuals)
ncvTest(fit2_08_07)

##Non Normality (model)
qqPlot(fit2_08_07, main = "Q-Q plot")
sresid08_07<-studres(fit2_08_07)
hist(sresid08_07, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid08_07<-na.omit(sresid08_07)
xfit<-seq(min(na.sresid08_07), max(na.sresid08_07), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_08_07)
qqPlot(fit2_08_07,main = "Q-Q Plot")
leveragePlots(fit2_08_07)


```
First model 2009-2008
```{r}
 #Model
fit09_08<- lm(df$CSR2009~df$`FCF/sales2008`+df$`FCF/employee2008`+df$ROE2008+df$`Net PM2008`+df$`Debt/Equity2008`+df$Sweden_dummy +df$Denmark_dummy + df$Finland_dummy + df$Norway_dummy)

#Stepwise regression
step09_08 <- stepAIC(fit09_08, direction="both")
step09_08$anova # display result

```
Second model 2009-2008

```{r}
#Model
fit2_09_08<-lm(df$CSR2009 ~ df$`FCF/sales2008` + df$`Net PM2008` + df$`Debt/Equity2008` + df$Denmark_dummy)
#Anova
print(Anova(fit2_09_08))

#Summary
print(summary(fit2_09_08))

# Autocorrelation
vif(fit2_09_08)
sqrt(vif(fit2_09_08))

##Non constant variance (Heteroscedasticity),
plot(fit2_09_08$residuals)
ncvTest(fit2_09_08)

##Non Normality (model)
qqPlot(fit2_09_08, main = "Q-Q plot")
sresid09_08<-studres(fit2_09_08)
hist(sresid09_08, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid09_08<-na.omit(sresid09_08)
xfit<-seq(min(na.sresid09_08), max(na.sresid09_08), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_09_08)
qqPlot(fit2_09_08,main = "Q-Q Plot")
leveragePlots(fit2_09_08)
```

First model 2010-2009
```{r}
  #Model
fit10_09<- lm(df$CSR2010~df$`FCF/sales2009`+df$`FCF/employee2009`+df$ROE2009+df$`Net PM2009`+df$`Debt/Equity2009`+df$Sweden_dummy +df$Denmark_dummy + df$Finland_dummy + df$Norway_dummy)

#Stepwise regression
step10_09 <- stepAIC(fit10_09, direction="both")
step10_09$anova # display result

```

Second model 2010-2009

```{r}
#Model
fit2_10_09<-lm(df$CSR2010 ~ df$`FCF/employee2009` + df$Denmark_dummy)
#Anova
print(Anova(fit2_10_09))

#Summary
print(summary(fit2_10_09))

# Autocorrelation
vif(fit2_10_09)
sqrt(vif(fit2_10_09))

##Non constant variance (Heteroscedasticity),
plot(fit2_10_09$residuals)
ncvTest(fit2_10_09)

##Non Normality (model)
qqPlot(fit2_10_09, main = "Q-Q plot")
sresid10_09<-studres(fit2_10_09)
hist(sresid10_09, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid10_09<-na.omit(sresid10_09)
xfit<-seq(min(na.sresid10_09), max(na.sresid10_09), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_10_09)
qqPlot(fit2_10_09,main = "Q-Q Plot")
leveragePlots(fit2_10_09)
```

First model 2011-2010

```{r}
#Model
fit11_10<- lm(df$CSR2011~df$`FCF/sales2010`+df$`FCF/employee2010`+df$ROA2010+df$ROE2010+df$`Net PM2010`+df$`Debt/Equity2010`+df$Sweden_dummy +df$Denmark_dummy + df$Finland_dummy + df$Norway_dummy)

#Stepwise regression
step11_10 <- stepAIC(fit11_10, direction="both")
step11_10$anova # display result

```
Second model 2011-2010

```{r}
#Model
fit2_11_10<-lm(df$CSR2011 ~ df$`FCF/employee2010` + df$`Debt/Equity2010` + df$Denmark_dummy)
#Anova
print(Anova(fit2_11_10))

#Summary
print(summary(fit2_11_10))

# Autocorrelation
vif(fit2_11_10)
sqrt(vif(fit2_11_10))

##Non constant variance (Heteroscedasticity),
plot(fit2_11_10$residuals)
ncvTest(fit2_11_10)

##Non Normality (model)
qqPlot(fit2_11_10, main = "Q-Q plot")
sresid11_10<-studres(fit2_11_10)
hist(sresid11_10, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid11_10<-na.omit(sresid11_10)
xfit<-seq(min(na.sresid11_10), max(na.sresid11_10), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_11_10)
qqPlot(fit2_11_10,main = "Q-Q Plot")
leveragePlots(fit2_11_10)
```

First model 2012 - 2011

```{r}
#Model
fit12_11<- lm(df$CSR2012~df$`FCF/sales2011`+df$`FCF/employee2011`+df$ROA2011+df$ROE2011+df$`Net PM2011`+df$`Debt/Equity2011`+df$Sweden_dummy +df$Denmark_dummy + df$Finland_dummy + df$Norway_dummy)

#Stepwise regression
step12_11 <- stepAIC(fit12_11, direction="both")
step12_11$anova # display result
```

Second model 2012 - 2011

```{r}
#Model
fit2_12_11<-lm(df$CSR2012 ~ df$`FCF/sales2011` + df$`Debt/Equity2011` + df$Denmark_dummy)
#Anova
print(Anova(fit2_12_11))

#Summary
print(summary(fit2_12_11))

# Autocorrelation
vif(fit2_12_11)
sqrt(vif(fit2_12_11))

##Non constant variance (Heteroscedasticity),
plot(fit2_12_11$residuals)
ncvTest(fit2_12_11)

##Non Normality (model)
qqPlot(fit2_12_11, main = "Q-Q plot")
sresid12_11<-studres(fit2_12_11)
hist(sresid12_11, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid12_11<-na.omit(sresid12_11)
xfit<-seq(min(na.sresid12_11), max(na.sresid12_11), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_12_11)
qqPlot(fit2_12_11,main = "Q-Q Plot")
leveragePlots(fit2_12_11)
```
First model 2013-2012

```{r}
#Model
fit13_12<- lm(df$CSR2013~df$`FCF/sales2012`+df$`FCF/employee2012`+df$ROA2012+df$ROE2012+df$`Net PM2012`+df$`Debt/Equity2012`+df$Sweden_dummy +df$Denmark_dummy + df$Finland_dummy + df$Norway_dummy)

#Stepwise regression
step13_12 <- stepAIC(fit13_12, direction="both")
step13_12$anova # display result

```
Second model 2013-2012

```{r}
#Model
fit2_13_12<-lm(df$CSR2013 ~ df$`FCF/sales2012` + df$`Debt/Equity2012` + df$Denmark_dummy)
#Anova
print(Anova(fit2_13_12))

#Summary
print(summary(fit2_13_12))

# Autocorrelation
vif(fit2_13_12)
sqrt(vif(fit2_13_12))

##Non constant variance (Heteroscedasticity),
plot(fit2_13_12$residuals)
ncvTest(fit2_13_12)

##Non Normality (model)
qqPlot(fit2_13_12, main = "Q-Q plot")
sresid13_12<-studres(fit2_13_12)
hist(sresid13_12, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid13_12<-na.omit(sresid13_12)
xfit<-seq(min(na.sresid13_12), max(na.sresid13_12), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_13_12)
qqPlot(fit2_13_12,main = "Q-Q Plot")
leveragePlots(fit2_13_12)
```

First model 2014-2013

```{r}
#Model
fit14_13<- lm(df$CSR2014~df$`FCF/sales2013`+df$`FCF/employee2013`+df$ROA2013+df$ROE2013+df$`Net PM2013`+df$`Debt/Equity2013`+df$Sweden_dummy +df$Denmark_dummy + df$Finland_dummy + df$Norway_dummy)

#Stepwise regression
step14_13 <- stepAIC(fit14_13, direction="both")
step14_13$anova # display result

```
Second model 2014-2013

```{r}
#Model
fit2_14_13<-lm(df$CSR2014 ~ df$`FCF/sales2013` + df$ROA2013 + df$ROE2013 + df$Sweden_dummy + df$Finland_dummy)
#Anova
print(Anova(fit2_14_13))

#Summary
print(summary(fit2_14_13))

# Autocorrelation
vif(fit2_14_13)
sqrt(vif(fit2_14_13))

##Non constant variance (Heteroscedasticity),
plot(fit2_14_13$residuals)
ncvTest(fit2_14_13)

##Non Normality (model)
qqPlot(fit2_14_13, main = "Q-Q plot")
sresid14_13<-studres(fit2_14_13)
hist(sresid14_13, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid14_13<-na.omit(sresid14_13)
xfit<-seq(min(na.sresid14_13), max(na.sresid14_13), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_14_13)
qqPlot(fit2_14_13,main = "Q-Q Plot")
leveragePlots(fit2_14_13)
```
First model 2015-2014

```{r}
#Model
fit15_14<- lm(df$CSR2015~df$`FCF/sales2014`+df$`FCF/employee2014`+df$ROA2014+df$ROE2014+df$`Net PM2014`+df$`Debt/Equity2014`+df$Sweden_dummy +df$Denmark_dummy + df$Finland_dummy + df$Norway_dummy)

#Stepwise regression
step15_14 <- stepAIC(fit15_14, direction="both")
step15_14$anova # display result

```
Second model 2015-2014

```{r}
#Model
fit2_15_14<-lm(df$CSR2015 ~ df$`FCF/sales2014` + df$ROA2014 + df$ROE2014 + df$`Debt/Equity2014` + df$Denmark_dummy)
#Anova
print(Anova(fit2_15_14))

#Summary
print(summary(fit2_15_14))

# Autocorrelation
vif(fit2_15_14)
sqrt(vif(fit2_15_14))

##Non constant variance (Heteroscedasticity),
plot(fit2_15_14$residuals)
ncvTest(fit2_15_14)

##Non Normality (model)
qqPlot(fit2_15_14, main = "Q-Q plot")
sresid15_14<-studres(fit2_15_14)
hist(sresid15_14, freq = FALSE, main = "Distribution of studentizised residuals")

na.sresid15_14<-na.omit(sresid15_14)
xfit<-seq(min(na.sresid15_14), max(na.sresid15_14), length= 40)
yfit<-dnorm(xfit)
lines(xfit, yfit)

#Outliers
outlierTest(fit2_15_14)
qqPlot(fit2_15_14,main = "Q-Q Plot")
leveragePlots(fit2_15_14)
```

